---
title: "Trends in Sephora Reviews — Data Cleaning and Prep"
author: "Camille Parker"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---


# Load packages

```{r}
library(tidyverse) ## Always load tidyverse
library(tidytext) ## Needed for text analysis
library(rstudioapi) ## set working directory
library(knitr) ## print nice tables
library(plotly) ## Interactive plots
library(RColorBrewer) ## Color palettes
```


# Set directory to wherever this script lives

```{r}
setwd(dirname(getActiveDocumentContext()$path))
```


# Load overall product info

```{r}
## List csv files
utils::unzip("sephora_data.zip", list = TRUE)$Name

## Load product info
product_info <- read_csv(unz("sephora_data.zip", "product_info.csv")) %>%
  select(product_id, reviews, primary_category, secondary_category, tertiary_category) %>% 
  mutate(category = ifelse(is.na(tertiary_category) == TRUE, secondary_category,
                           tertiary_category))
```


# Which categories have the most reviews?

```{r}
product_info %>% 
  group_by(category) %>% 
  summarize(reviews = sum(reviews, na.rm = TRUE)) %>% 
  arrange(desc(reviews)) %>% 
  head(10) %>% 
  kable()
```


# Load individual reviews

```{r}
reviews <- utils::unzip("sephora_data.zip", list = TRUE)$Name %>%
  str_subset("^reviews_.*\\.csv$") %>%
  map_dfr(~ read_csv(unz("sephora_data.zip", .x), 
                     show_col_types = FALSE,
                     col_select = c(product_id, product_name, brand_name,
                                    submission_time, rating, is_recommended,
                                    review_title, review_text))) %>% 
  mutate(year = as.numeric(substr(submission_time, 1, 4))) %>%
  distinct() %>% 
  inner_join(product_info, by = "product_id")
```


# Recount categories with highest number of reviews

```{r}
reviews %>% 
  group_by(category) %>% 
  summarize(reviews = n()) %>% 
  arrange(desc(reviews)) %>% 
  head(10) %>% 
  kable()
```


# Make files for type

```{r}
## Pick subtype
subtype_reviews <- reviews %>% filter(category == "Moisturizers")

## Merge the title of the review with the actual review, and unnest tokens
tokens <- subtype_reviews %>%
  unite("review_title_and_test", review_title, review_text, sep = " ") %>%
  unnest_tokens(word, review_title_and_test) 

## Count use of each token, and average across ratings/recommendation given
token_counts <- tokens %>%
  group_by(word) %>% 
  summarise(n = n(),
            average_rating = mean(rating, na.rm=TRUE), 
            average_recommendation = mean(is_recommended, na.rm=TRUE)) %>%
  arrange(-n) %>% 
  filter(n>200)

## Group word use by year
token_counts_year <- tokens %>%
  group_by(word, year) %>%
  summarise(n = n(),
            average_rating = mean(rating, na.rm = TRUE),
            average_recommendation = mean(is_recommended, na.rm = TRUE)) %>% 
  arrange(-n)%>% 
  filter(n>20) %>% ## keep words used more than 20x per year
  group_by(word) %>%
  filter(n() > 10) %>% ## keep words that had substantial use more than half of the years
  ungroup()
```


# Look at distribution of word counts

```{r}
token_counts %>% 
  ggplot(aes(n)) + 
  geom_histogram(fill="cornflowerblue") + 
  geom_vline(aes(xintercept = mean(n, na.rm=TRUE)), lty = 2) +
  geom_vline(aes(xintercept = median(n, na.rm=TRUE))) +
  scale_x_log10(labels = function(x) format(x, scientific = FALSE)) +
  labs(title = "Word Counts", subtitle = "solid line = median; dotted line = mean")+
  theme_classic()
```


# Look at how key words are distributed accross average rating

Good sanity check to see if desirable words float to the top, etc.

```{r}
token_counts %>%
  anti_join(get_stopwords()) %>%
  filter(str_detect(word, "[A-Za-z]")) %>% 
  filter(nchar(word) > 1) %>% 
  filter(n > 100) %>% 
  ggplot(aes(n, average_rating)) +
  geom_text(aes(label = word), check_overlap = TRUE, show.legend = FALSE, vjust = "top", hjust = "left") +
  scale_x_log10(labels = function(x) format(x, scientific = FALSE)) +
  theme_classic()
```


# Run linear models and extract results

```{r}
linear_slopes <- token_counts_year %>%
  group_by(word) %>%
  do(model = lm(average_rating ~ year, data = .)) %>%
  filter(!is.null(model)) %>%
  summarize(word = word[1],
            slope = coef(model)[2],
            intercept = coef(model)[1], 
            significance = ifelse(nrow(summary(model)$coefficients) >= 2 & 
                                  ncol(summary(model)$coefficients) >= 4,
                                  summary(model)$coefficients[2, 4], NA)) %>%
  ungroup()
```


# Select words with highest and lowest linear coefficients

In other words, which keywords have the largest decline or increase in associated rating?

```{r}
declining_words <- linear_slopes %>% 
  arrange(slope) %>% 
  head(n = 5) %>%
  select(word, slope)

ascending_words <- linear_slopes %>% 
  arrange(slope) %>% 
  tail(n = 5) %>%
  select(word, slope)

shifting_words <- rbind(declining_words, ascending_words) %>% 
  arrange(-slope)
```


# Time to plot!

```{r}
## Set up some nice colors
colour_map <- set_names(rev(colorRampPalette(brewer.pal(10, "RdYlGn"))(10)),
                        shifting_words$word)

## Make sure plot legend stays in order of coefs (not alphabetical)
word_order <- shifting_words$word

## Set up plot
token_trajectories <- shifting_words %>%
  inner_join(token_counts_year) %>% 
  mutate(word = factor(word, levels = word_order)) %>% 
  ggplot(aes(x = year, y = average_rating, group = word, color = word)) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_manual(values = colour_map) +
  scale_x_continuous(breaks = c(2008,2010,2012,2014,2016,2018,2020,2022))+
  scale_y_continuous(limits = c(1,5),
                     breaks = c(1,2,3,4,5))+
  labs(x = "Year",
       y = "Average Rating",
       color = "Keyword",
       title = "Trends in Ratings of Moisturizers") +
  theme_bw()

## Make interactive
ggplotly(token_trajectories)
```


# Let's take a closer look at one of our keywords

```{r}
subtype_reviews %>% 
  filter(year >= 2022 & 
           rating == 5 &
           str_detect(review_text, "packaging")) %>% 
  sample_n(3) %>% 
  select(review_text) %>% 
  kable()
```

